Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-11 paper/paper.tex
correction in text

Generational fuzzers are typically grammar-based. These fuzzers
generate a new file using the grammar of the language whose inputs
should be fuzzed. Intuitively, those fuzzers implement a traversal of
the production rules of the input grammar to create syntax trees,
which are then pretty-printed. Consequently, this approach produces
inputs that are syntactically valid by construction.  We analyzed two
grammar-based fuzzers--Grammarinator~\cite{grammarinator} and
QuickFuzz~\cite{quickfuzz,grieco2016quickfuzz}.  Unfortunately none
was effective out of the box. Given the bound limits we defined on the
number of inputs to generate and the depth of exploration in the
syntax tree, we were unable to find discrepancies on the inputs those
tools generated. To sum, the tools produced a high percentage of
semantically-invalid inputs (\eg{}, \Fix{give one or two concrete
  examples--variable usage without definition?}) that we needed to
discard and the valid inputs manifested no discrepancies. For example,
we produced 10K inputs with Grammarinator and only \Fix{X} of those
were valid. With QuickFuzz, we were able to produce \Fix{Y, Y$>$Y?}
valid inputs as it contains some heuristics to circumvent violation of
certain type rules such as \Fix{variable used must be
  defined?}. Nonetheless, running those inputs in our infrastructure
we were unable to find discrepancies. Inpecting those inputs, we
realized that they reflected very simple scenarios. \Mar{are there
  weights associated with production rules besides the depth you can
  set?} To sum, we did not consider this kind of fuzzer in this
study\Fix{...}

@@

Mutational fuzzers can be either white-box or
black-box. White-box mutational fuzzers are typically
coverage-based. American Fuzz Loop
(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of
this kind of fuzzers. These fuzzers run tests inputs
against instrumented versions of the program under testing with the
typical goal of finding univeral errors like crashes and buffer
overflows. The instrumentation adds code to collect branch coverage and
monitor specific properties\footnote{There are options in the clang
  toolchain to build programs with fuzzing
  instrumentation~\cite{libfuzzer}. clang provides several sanitizers
  for property checking~\cite{clang-documentation}.}. The typical
approach to input generation is evolutionary--these fuzzers try to
minimize the distances to still-uncovered branches of the
program. AFL, for instance, takes the instrumented program binary
(say, a JS engine) and one seed input to that program (say, a JS
program) and produces on output fault-revealing inputs, if
found. Considering our context of application, we needed to instrument
one runtime engine for fuzzing; we chose v8. Unfortunately, we found
that most of the inputs produced by AFL violate the JS
grammar. Furthermore, the fuzzing task took days, even when considering
only one seed and there is no simple way to guide the
exploration. That happens because the fuzzer aims to explore the
entire decision tree induced from the engine's main function,
including the branches associated with the lexer and the parser. For
those reasons, coverage-based fuzzers were not considered in this
study. It is worth mentioning that Google mitigates that problem by
promoting developers to create fuzz targets for specific program
functions\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although that approach has shown very effective,
it requires domain knowledge to create the calling context to invoke
the fuzz target.

>>>>

Generational fuzzers are typically grammar-based. These fuzzers
generate a new file using the grammar of the language whose inputs
should be fuzzed. Intuitively, those fuzzers implement a traversal of
the production rules of the input grammar to create syntax trees,
which are then pretty-printed. Consequently, this approach produces
inputs that are syntactically valid by construction.  We analyzed
three grammar-based fuzzers--Grammarinator~\cite{grammarinator},
jsfunfuzz~\cite{jsfunfuzz}, and
QuickFuzz~\cite{quickfuzz,grieco2016quickfuzz}.  Unfortunately, none
of those was effective out of the box. Given the bound limits we
defined on the number of inputs to generate and the exploration depth
of the syntax tree, we were unable to find discrepancies on the inputs
those tools generated. To sum, the tools produced a high percentage of
semantically-invalid inputs (\eg{}, \Fix{give one or two concrete
  examples--variable usage without definition?}) that we needed to
discard and the valid inputs manifested no discrepancies. For example,
we produced 100K inputs with Grammarinator and only \Fix{X} of those
were valid. With QuickFuzz, we were able to produce \Fix{Y, Y$>$Y?}
valid inputs as it contains some heuristics to circumvent violation of
certain type rules such as \Fix{variable used must be
  defined?}. Nonetheless, running those inputs in our infrastructure
we were unable to find discrepancies. Inpecting those inputs, we
realized that they reflected very simple scenarios.\Comment{ \Mar{are there
  weights associated with production rules besides the depth you can
  set?}} Although grammar-based fuzzers has been shown effective to
find real bugs\Fix{cite some jsfunfuzz bug reports}, generating
valid inputs is very time-consuming, especially for the context of
differential testing. For this reason, we did not consider those fuzzers.

@@

Mutational fuzzers can be either white-box or black-box. White-box
mutational fuzzers are typically coverage-based. American Fuzz Loop
(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
kind of fuzzers. These fuzzers run tests inputs against instrumented
versions of the program under testing with the typical goal of finding
univeral errors like crashes and buffer overflows. The instrumentation
adds code to collect branch coverage and to monitor specific
properties\footnote{There are options in the clang toolchain to build
  programs with fuzzing instrumentation~\cite{libfuzzer}. clang
  provides several sanitizers for property
  checking~\cite{clang-documentation}.}. AFL use coverage to determine
inputs that uncover a new branch and deserve fuzzing whereas libFuzzer
uses evolutionary generation--it tries to minimize the distances to
still-uncovered branches of the program. AFL takes the instrumented
program binary (say, a JS engine) and one seed input to that program
(say, a JS program) and produces on output fault-revealing inputs, if
found. Considering our context of application, we needed to instrument
one runtime engine for fuzzing; we chose v8. Unfortunately, we found
that most of the inputs produced by AFL violate the JS
grammar. Furthermore, the fuzzing task can take daysfor a single seed
input and there is no simple way to guide the
exploration~\Fix{cite}. That happens because the fuzzer aims to
explore the entire decision tree induced from the engine's main
function, including the branches associated with the lexer and the
parser. For those reasons, coverage-based fuzzers were not considered
in this study. It is worth mentioning that Google mitigates that
problem with libFuzzer by asking developers to create fuzz targets for
specific program
functions\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
that approach has shown very effective, it requires domain knowledge
to create the calling context to invoke the fuzz target.
